JD notes on effects

### 2022-07-30 manuscript/body.tex
Sending back to JD

\item [Focal model center] The average of the linear predictor variables corresponding to the focal predictor. The average of the linear predictor variables corresponding to the non-focal predictor(s) is \emph{non-focal model center}. For simple continuous input variables, averaging linear predictor variables is the same as averaging the input variables (see \FREF{justify_plots}). Focal and non-focal model center values is also referred to as \emph{center point}. 
\jd{I don't like this as a separate item. What is the need?}
\BC{\fix{We need the terms to talk about model center \dots}}

\item [Model center] Is the value of the central estimate calculated using focal and non-focal model center values (center point). It is a calculation that is equal to the average of central estimates for a linear model (identity link function) without complex interactions.

@@

\BC{\fix{Discuss with JD}}

\jd{We should maybe discuss mediated effects and other stuff. We need to be much clearer about chains of causality and this example. Let's not say “somehow”}
A \emph{mediated} effect is a situation in which only some of the input variables have a \emph{causal} impact on the outcome, even though all the variables are associated with the outcome. For example, psychological factors such as water taste in the relationship between household socio-economic status and improved water quality status.
\jd{Maybe a good example for this would be using education as a mediator for effects of wealth? Can you think of a better one?}
\BC{\fix{Discuss with JD}}

For simplicity, we consider a hypothetical simulation for three variables: input variables $x$ and $y$; and outcome variable $z$; such that
%
\begin{center}
\begin{tikzpicture}
    \node (1) at (0,0) {x};
    \node (2) [right = of 1] {y};
    \node (3) [below = of 2] {z};
    \path (1) edge  (2);
    \path (1) edge (2);
    \path (2) edge (3);
    \path (1) edge (3);
\end{tikzpicture}
\end{center}
%
The arrows above show the direction of influence, and the implication of $x\rightarrow y$ and $y \rightarrow z$ is that $x$ affects $z$ in two ways. First, it has (some) direct effect; second, it can have an indirect effect by influencing $y$, regulated by parameter $\rho$ as shown in \nameref{S3_Appendix}.

>>>>

\item [Model center] Is the value of the central estimate calculated using focal and non-focal model center values. It is a calculation that is equal to the average of central estimates for a linear model (identity link function) without complex interactions. The average of the linear predictor variables corresponding to the focal non-focal predictors are the focal and non-focal model center. Focal and non-focal model center values is also referred to as \emph{center point}. For simple continuous input variables, averaging linear predictor variables is the same as averaging the input variables (see \FREF{justify_plots}).

@@

To illustrate this, consider an example in which age of the head of the household (\code{x}) has a direct on the availability of improved water service in the household (\code{z}), as well as an indirect effect through its effect on the income of the head of the household (\code{y}), as illustrated below:
%
\begin{center}
\begin{tikzpicture}
    \node (1) at (0,0) {x};
    \node (2) [right = of 1] {y};
    \node (3) [below = of 2] {z};
    \path (1) edge  (2);
    \path (1) edge (2);
    \path (2) edge (3);
    \path (1) edge (3);
\end{tikzpicture}
\end{center}
%
The arrows above show the direction of influence, and the implication of $x\rightarrow y$ and $y \rightarrow z$ is that $x$ affects $z$ in two ways. First, it has direct effect; second, it can have an indirect effect by influencing $y$, regulated by parameter $\rho$ as shown in \nameref{S3_Appendix}.
